Democracy, Public Support, and Measurement Uncertainty

### 2021-08-13 paper/dcpo_demsupport.Rmd
avoid nested script calls by incorporating needed broom_utilities in tidy_pgmm

load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda"))
load(here("data", "expcor_cls_ajps.rda"))
load(here("data", "expcor_cls_apsr.rda"))
load(here("data","claassen_replication_input.rda"))
load(here("data","exp_claassen_input.rda"))
load(here("data","dcpo_apsr.rda"))
load(here("data","dcpo_ajps.rda"))

>>>>

load(here("data", "correct_cls_ajps.rda")) # https://osf.io/52u7n/download
load(here("data", "correct_cls_apsr.rda")) # https://osf.io/2hwqg/download
load(here("data", "expcor_cls_ajps.rda"))  # https://osf.io/wfm3c/download
load(here("data", "expcor_cls_apsr.rda"))  # https://osf.io/rvc92/download
load(here("data","claassen_replication_input.rda"))
load(here("data","exp_claassen_input.rda"))
#load(here("data","dcpo_apsr.rda"))
#load(here("data","dcpo_ajps.rda"))
